Astrophysical calibration of gravitational-wave detectors

### 2016-02-04 docs/cosmic_cal.tex
Updated response to comment about plots

\begin{figure*}
 \begin{center}
  \includegraphics[width=1.0\textwidth]{bns_post_fig.pdf}
 \end{center}
 \caption{\label{fig:bnspost} The marginalised posterior probability distributions for some of the unknown
 parameters of a \ac{BNS} system, including calibration scaling factors (surrounded by the red 
borders) for the three detectors (H1, L1 and V1). The simulated signal was at a distance of 
250\,Mpc, had \ac{SNR} of 7.9, 9.2 and 5.2 and percentage relative uncertainties in the calibration scale 
factors of 17\%, 15\% and 24\% for each of the detectors respectively.}
\end{figure*}

\begin{figure*}
 \begin{center}
  \includegraphics[width=1.0\textwidth]{nsbh_post_fig.pdf}
 \end{center}
 \caption{\label{fig:nsbhpost} The marginalised posterior probability distributions for some of the unknown
 parameters of a \ac{NSBH} system, including calibration scaling factors for the three detectors 
(H1, L1 and V1). The simulated signal was at a distance of 450\,Mpc, had \ac{SNR} of 9.8, 10.3 and 
3.8 and percentage relative uncertainties in the calibration scale factors of 15\%, 14\% and 36\% for each of 
the detectors respectively.}
\end{figure*}

>>>>

\begin{figure*}
 \begin{center}
  \includegraphics[width=1.0\textwidth]{bns_post_fig.pdf}
 \end{center}
 \caption{\label{fig:bnspost} The marginalised posterior probability distributions for some of the unknown
 parameters of a \ac{BNS} system, including calibration scaling factors (surrounded by the 
\refresp{thicker} red 
borders) for the three detectors (H1, L1 and V1). The simulated signal was at a distance of 
250\,Mpc, had \ac{SNR} of 7.9, 9.1 and 5.2 and percentage relative uncertainties in the calibration 
scale factors of 15\%, 14\% and 22\% for each of the detectors respectively.}
\end{figure*}

\begin{figure*}
 \begin{center}
  \includegraphics[width=1.0\textwidth]{nsbh_post_fig.pdf}
 \end{center}
 \caption{\label{fig:nsbhpost} The marginalised posterior probability distributions for some of the unknown
 parameters of a \ac{NSBH} system, including calibration scaling factors for the three detectors 
(H1, L1 and V1). The simulated signal was at a distance of 450\,Mpc, had \ac{SNR} of 9.7, 10.3 and 
3.8 and percentage relative uncertainties in the calibration scale factors of 14\%, 13\% and 43\% 
for each of the detectors respectively.}
\end{figure*}
